Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}

### 2017-11-13 paper/method.tex

\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.}

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
\CHANGED{For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries. These boundaries are then individually rated using our split error classifier.}

@@

\CHANGED{Fig. \ref{fig:merge_error} illustrates this procedure. Pseudo code is available as supplemental material to promote understanding.}

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$.

@@

\subsection{User Interface}

We integrate guided proofreading into an existing large data connectomics workflow. The web-based system is designed with a novice-friendly user interface (Fig.~\ref{fig:ui}). We show the current labeling of a cell boundary outline and its proposed correction overlayed on EM image data. The user cannot distinguish the current labeling from the proposed correction to avoid selection bias. We also show a solid overlay of the current and the proposed labeling. In addition, we show the image without overlays to provide an unoccluded view. User interaction is simple and involves one mouse click on either the current labeling or the correction. After interaction, the next potential error is shown.

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{User interface. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
\label{fig:ui}
\end{figure}

>>>>

\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
If the classifier yields a result close to 0, the candidate split is likely to be correct. We then use it to fix the merge error.}

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
\CHANGED{%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
As preprocessing, we dilate the label by 20 pixel which is motivated by our observation that the generated splits tend to attach to real membrane boundaries. These boundaries are then individually rated using our split error classifier. Fig. \ref{fig:merge_error} illustrates this procedure. Pseudo code is available as supplemental material to promote understanding.}

@@

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$. \CHANGED{Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{\CHANGED{Example error correction within the forced choice setting.} A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
\label{fig:ui}
\end{figure}

### 2017-11-13 paper/supplemental/cremi.tex

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the CREMI A dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $5.4\times$ higher than GP (as indicated by the arrow), with median VI of $5.32$ and $SD=0.009$. GP does not reach the best possible VI as discussed in the text.}
\label{fig:cremiAboxplot}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiBboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across 5 sections of the CREMI B dataset. We compare automatic selection and oracle selection. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.25$ and $SD=0.07$.}
\label{fig:cremiBboxplot}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across the CREMI C subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (as indicated by the arrow), with median VI of $4.81$ and $SD=0.08$.}
\label{fig:cremiCboxplot}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the CREMI A dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $5.4\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $5.32$ and $SD=0.009$. GP does not reach the best possible VI as discussed in the text.}
\label{fig:cremiAboxplot}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiBboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across 5 sections of the CREMI B dataset. We compare automatic selection and oracle selection. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $4.25$ and $SD=0.07$.}
\label{fig:cremiBboxplot}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across the CREMI C subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $3\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $4.81$ and $SD=0.08$.}
\label{fig:cremiCboxplot}
\end{figure}

### 2017-11-13 paper/supplemental/leftcylinder.tex

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cylboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.~Cylinder dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}
\label{fig:cylboxplot}
\end{figure}

@@

\CHANGED{In the paper, we use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cylboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L.~Cylinder dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (\protect\includegraphics[width=0.2cm]{gfx/arrow.pdf}), with median VI of $2.75$ and $SD=0.789$.}
\label{fig:cylboxplot}
\end{figure}

@@

\CHANGED{We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA~\cite{shaffer1995}) followed by parametric tests (Welch's t-test~\cite{welch}).}
